---
title: "Statistical Inference Project Part 2"
author: "Ryan Wissman"
date: "Sunday, January 25, 2015"
output: pdf_document
---

#Coursera Statistical Inference Course Project

This is part two of the project for the class on statistical inference. For this project we will be analyzing the ToothGrowth dataset found in R. We will address the following questions using this data:

1) Load the ToothGrowth data and perform some basic exploratory data analyses 
2) Provide a basic summary of the data.
3) Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)
4) State your conclusions and the assumptions needed for your conclusions. 

##Loading data and initial analysis

Load the data.

```{r}
library(datasets)
data(ToothGrowth)

#Get the first few rows of the data
head(ToothGrowth)
```

The data shows the effect of vitamin c on tooth growth in guinea pigs. We know that the length of the tooth is given by (len), as well as the delivery method (OJ) or (VC), and the three dose levels (.5, 2, and 2mg). A great way to quickly visualize this data would be to create a box and whisker plot illustrating the tooth growth by dosage level and delivery method.

```{r}


```

